An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling

### 2017-05-10 paper.tex
Fix grammar errors

    A new tool to visualize scheduling visualize is developed, enabling developers to record the scheduler states
    including executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution,
    scheduling events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g.
    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. It gathers entire
    activities inside Linux kernel in microsecond scale, being able to capture the impact of occasional short-burst
    scheduler events, which only last less that 10us. These events are mostly not shown in the result of sampling based
    measurement which focus on average-case execution time. By analyzing full-detailed record, we can not only
    capture the worst-case execution time (WCET), but also understand the cause of these incidents.

@@

    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WCET of 27us and 17us. With these result, we are
    able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
    applications as kernel modules. But this is tedious and making the debugging process difficult. Thus, we proposed a
    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}, allowing userspace programs running in kernel
    address space. Thus, system calls become jump instructions instead of instructions that traps the processor. Also,
    this would mitigate the cache contention while switching in and out the kernel during system call.
    In addition, we have wrapped system calls with vDSO \cite{vDSO} for better compatibility. It results in
    user-space program running in KML with WCET similar to Linux kernel module variants.

>>>>

    A new tool to visualize scheduling is developed, enabling developers to record the scheduler states
    including executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution,
    scheduling events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g.
    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. It gathers entire
    activities inside Linux kernel in microsecond scale, being able to capture the impact of occasional short-burst
    scheduler events, which only last less that 10us. These events are mostly not shown in the result of sampling based
    measurement which focus on average-case execution time. By analyzing full-detailed record, we can not only
    capture the worst-case execution time (WCET), but also understand the cause of these incidents.

@@

    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WCET of 27us and 17us. With these results, we are
    able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
    applications as kernel modules. But this is tedious and making the debugging process difficult. Thus, we proposed a
    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}, allowing userspace programs running in kernel
    address space. Thus, system calls become jump instructions instead of instructions that traps the processor. Also,
    this would mitigate the cache contention while switching in and out the kernel during system call.
    In addition, we have wrapped system calls with vDSO \cite{vDSO} for better compatibility. It results in
    user-space program running in KML with WCET similar to Linux kernel module variants.
